\documentclass[12pt,a4paper]{article}

% Required packages for official document formatting
\usepackage{geometry}
\usepackage{array}
\usepackage{booktabs}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{pifont}

% Set proper margins for official documents
\geometry{
    left=1in,
    right=1in,
    top=1in,
    bottom=1in
}

% Define custom colors for official document
\definecolor{govblue}{RGB}{0,51,102}
\definecolor{govgray}{RGB}{102,102,102}
\definecolor{accentgreen}{RGB}{0,128,0}
\definecolor{accentred}{RGB}{178,34,34}

% Remove paragraph indentation
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}

% Header and footer setup
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\rfoot{Page \thepage\ of \pageref{LastPage}}

% Custom commands for official formatting
\newcommand{\talkingheader}[1]{\textbf{\color{govblue}#1}}
\newcommand{\keymessage}[1]{\textbf{\color{accentgreen}\ding{226} #1}}
\newcommand{\supporting}[1]{\textit{#1}}
\newcommand{\question}[1]{\textbf{Q: #1}}
\newcommand{\answer}[1]{\textbf{A:} #1}
\newcommand{\handle}[1]{\textcolor{accentred}{\textbf{Handle:} #1}}

\begin{document}

% Document Header
\begin{center}
    {\large \textbf{TALKING POINTS}}
\end{center}

\vspace{0.3cm}

\begin{table}[h]
\centering
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Meeting Type:} & Press Conference on Financial Reforms \\
\textbf{Date:} & 27.10.2025 \\
\textbf{Subject:} & New Financial Reporting Guidelines Implementation \\
\textbf{Prepared for:} & Secretary, Department of Economic Affairs \\
\textbf{Prepared by:} & Media Relations Division \\
\bottomrule
\end{tabular}
\end{table}

\vspace{0.5cm}

\talkingheader{KEY MESSAGES}

\begin{enumerate}[leftmargin=*, itemsep=8pt]
    \item \keymessage{Historic Financial Reform}
    \supporting{First major overhaul of public financial management since 2010, bringing India in line with international standards and enhancing transparency in government operations}

    \item \keymessage{Digital Transformation of Financial Management}
    \supporting{Integration of accrual-based accounting with real-time digital reporting, enabling Parliament and public to access government financial data through secure online portals}

    \item \keymessage{Economic Benefits and Efficiency Gains}
    \supporting{Projected savings of Rs. 150 crore annually through improved financial governance, reduced delays, and better resource allocation across government departments}
\end{enumerate}

\vspace{0.5cm}

\talkingheader{SUPPORTING DATA AND FACTS}

\begin{table}[h]
\centering
\begin{tabular}{@{}lr@{}}
\toprule
\textbf{Parameter} & \textbf{Value} \\
\midrule
Ministries/Departments covered & 58 \\
Total financial transactions annually & 18.5 million \\
Initial investment & Rs. 245 crore \\
Annual recurring costs & Rs. 78 crore \\
Expected efficiency savings & Rs. 150 crore/year \\
Implementation timeline & 12 months (phased) \\
\bottomrule
\end{tabular}
\end{table}

\vspace{0.3cm}

\subsection*{Key Statistics to Highlight:}
\begin{itemize}[leftmargin=*, itemsep=3pt]
    \item[\ding{226}] \textbf{Transparency Improvement:} From annual to quarterly financial reporting
    \item[\ding{226}] \textbf{International Standards:} Compliance with IPSAS and IMF best practices
    \item[\ding{226}] \textbf{Digital Integration:} Seamless PFMS and IFMS system connectivity
    \item[\ding{226}] \textbf{Capacity Building:} Training for 15,000+ finance officers nationwide
\end{itemize}

\vspace{0.5cm}

\talkingheader{POTENTIAL QUESTIONS AND RESPONSES}

\begin{enumerate}[leftmargin=*, itemsep=8pt]
    \item \question{Why is this reform necessary now?}
    \answer{Current financial reporting framework is 15 years old and inadequate for modern governance needs. The reform responds to Fifteenth Finance Commission recommendations and aligns with Digital India initiatives.}

    \item \question{What are the main benefits for taxpayers?}
    \answer{Enhanced transparency allows citizens to track government spending, reduces financial waste through better oversight, and improves service delivery through efficient resource allocation.}

    \item \question{How will this affect different government departments?}
    \answer{Standardized reporting will make inter-departmental comparisons possible, identify best practices, and enable better coordination of national financial programs.}

    \item \question{What about the costs involved?}
    \answer{The investment of Rs. 245 crore is modest compared to annual benefits of Rs. 150 crore in efficiency savings. The reform pays for itself within two years.}

    \item \question{How will you ensure data security and privacy?}
    \answer{Multiple layers of security including end-to-end encryption, multi-factor authentication, and regular audits by CERT-In empaneled agencies ensure complete data protection.}
\end{enumerate}

\vspace{0.5cm}

\talkingheader{BACKGROUND CONTEXT}

\begin{itemize}[leftmargin=*, itemsep=4pt]
    \item \textbf{Development Timeline:} Guidelines developed over 18 months with consultation from CAG, IMF, ICAl, and 58 ministries
    \item \textbf{International Benchmarking:} Based on best practices from USA, UK, Australia, and Canada
    \item \textbf{Legal Framework:} Empowered by Finance Act 2024 and Article 112 of the Constitution
    \item \textbf{Digital Infrastructure:} Leverages existing PFMS platform with enhanced capabilities
\end{itemize}

\vspace{0.5cm}

\talkingheader{IMPORTANT NOTES FOR SECRETARY}

\subsection*{Emphasis Points:}
\begin{itemize}[leftmargin=*, itemsep=3pt]
    \item[\ding{48}] \textbf{Transformational Nature:} This is not just an administrative change but a fundamental shift in financial governance
    \item[\ding{48}] \textbf{International Recognition:} IMF and World Bank have acknowledged this as a significant reform
    \item[\ding{48}] \textbf{Political Consensus:} All-party support for enhanced financial transparency
    \item[\ding{48}] \textbf{Federal Cooperation:} State governments also being consulted for broader adoption
\end{itemize}

\subsection*{Sensitive Topics to Handle Carefully:}
\begin{itemize}[leftmargin=*, itemsep=3pt]
    \item[\ding{55}] \handle{Implementation Challenges:} Frame as manageable rather than problematic}
    \item[\ding{55}] \handle{Timeline Questions:} Emphasize phased approach to ensure quality}
    \item[\ding{55}] \handle{Budgetary Impact:} Focus on long-term savings and efficiency gains}
    \item[\ding{55}] \handle{State Government Coordination:} Highlight collaborative approach}
\end{itemize}

\vspace{0.5cm}

\talkingheader{QUICK REFERENCE FACTS}

\begin{multicols}{2}
\subsection*{Implementation Timeline:}
\begin{itemize}[leftmargin=*, itemsep=2pt]
    \item[\ding{51}] Jan-Mar 2026: System preparation
    \item[\ding{51}] Apr-Sep 2026: Pilot implementation
    \item[\ding{51}] Oct 2026: Full rollout
\end{itemize}

\columnbreak

\subsection*{Key Stakeholders:}
\begin{itemize}[leftmargin=*, itemsep=2pt]
    \item[\ding{51}] 58 Ministries/Departments
    \item[\ding{51}] 247 Autonomous Bodies
    \item[\ding{51}] 42 Public Sector Enterprises
    \item[\ding{51}] 15,000+ Finance Officers
\end{itemize}
\end{multicols}

\vspace{0.3cm}

\subsection*{International Recognition:}
\begin{itemize}[leftmargin=*, itemsep=2pt]
    \item[\ding{52}] IMF Technical Assistance Program
    \item[\ding{52}] World Bank Governance Review
    \item[\ding{52}] OECD Public Governance Committee
    \item[\ding{52}] Asian Development Bank Knowledge Sharing
\end{itemize}

\vspace{0.5cm}

\talkingheader{CONTACT INFORMATION}

\begin{table}[h]
\centering
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{For Media Queries:} & \\
\textbf{Spokesperson:} & Joint Secretary (Budget) \\
\textbf{Email:} & media.dea@gov.in \\
\textbf{Phone:} & 011-23742301 \\
\textbf{Website:} & www.finmin.nic.in/dea \\
\bottomrule
\end{tabular}
\end{table}

\vspace{0.5cm}

\begin{center}
    {\small \textit{These talking points are for official use and should be adapted based on specific audience and context.}}
\end{center}

\vspace{0.3cm}

\begin{flushright}
    \textbf{(Media Relations Division)}\\
    \textit{Department of Economic Affairs}\\
    \textit{Ministry of Finance}\\
    \textit{27.10.2025}
\end{flushright}

\end{document}